\documentclass{article}
\usepackage{fontspec}
\usepackage{lilyglyphs}
\usepackage{gchords}
\usepackage{hyperref}
\usepackage[chorded]{songs}
\newindex{titleidx}{cbtitle}

\begin{document}
\setlength{\parindent}{0pt}


\section{Paul Kelly - How To Make Gravy}

Listen here: \url{https://www.youtube.com/watch?v=iYqIF2XkqKU}

This is a good beginner song for many reasons:

\begin{itemize}
    \item It doesn't need \textit{bar chords}
    \item It's easy to strum because you always play all six strings
    \item The only finger that comes off the fretboard is the middle finger
    \item You're constantly sliding your fretting hand up and down the neck, which will get you some big, juicy calluses
    \item It's a Christmas song
    \item It's written by an Australian
    \item It sounds good
\end{itemize}


There are only two chord shapes needed, E major and E minor.  These are moved up and down the neck while playing open E and B strings.  This effect, where one or more strings plays the same note continuously, is called a \textbf{drone}.

\subsection{Chords Used}

\def\numfrets{5}
\mediumchords

\chords{
    \chord{t}{o,f3p2,f4p2,f2p1,o,o}{E}
    \chord{t}{o,f3p4,f4p4,f1p2,o,o}{F\textsuperscript{\sharp{}}m}
    \chord{3}{o,f3p3,f4p3,f1p1,o,o}{G\textsuperscript{\sharp{}}m}
    \chord{4}{o,f3p2,f4p2,f2p1,o,o}{A}
    \chord{6}{o,f3p2,f4p2,f2p1,o,o}{B}
}

\subsection{The Song}

The first two verses are overleaf, the chords just repeat throughout the rest.

\bigskip

The strumming pattern will be difficult to begin with, just strum whatever rhythm you want, straight fours will do.

\begin{songs}{titleidx}
\beginsong{How To Make Gravy}[
    by={Paul Kelly}]
\beginverse
\[E]Hello Dan, it's \[F#m]Joe here.
\[G#m]I hope you're keeping \[F#m]well.
\[E]It’s the 21st of Dec\[F#m]ember,
\[G#m]now they’re ringing the last \[F#m]bell.
\[A]If I get good be\[G#m]haviour
\[A]I'll be out of here by Ju\[B]ly.
\[E]Won’t you kiss my kids on \[F#m]Christmas day?
\[G#m]Please \[F#m]don't let them cry.\[E]
\endverse
\beginverse
^I guess the brothers are driving down from ^Queensland
^and Stella's flying in from the ^coast.
^They say it's gonna be a hundred ^degrees, even more maybe,
^but that won't ^stop the roast.
^Who's gonna make the ^gravy now?
^I bet it won't taste the ^same.
^Just add flour, salt, ^a little red wine and don't forget a
^dollop of tomato sauce for sweetness ^and that extra tang.
\endverse
\endsong
\end{songs}

\end{document}
